The Hydrogen Epoch of Reionization Array Dish: Beam Pattern Measurements and Science Implications

### 2015-11-04 DishMeasurements/memo/DishBeamMeasurementsPaper.tex
working on dish beam paper

%\documentclass{emulateapj}
\documentclass[preprint]{aastex}

@@

%\shorttitle{HERA Dish Beam Measurements Memo, Rev $\alpha$}
%\shortauthors{Neben}

@@

\title{HERA Dish Beam Measurements Memo}

@@

\author{Abraham Neben, Rich Bradley, Jackie Hewitt, others}
%\affil{MIT Kavli Institute, Massachusetts Institute of Technology, Cambridge, MA, 02139 USA}

\author{Oct 26, 2015}

@@

%\keywords{instrumentation: interferometers --- techniques: interferometric --- cosmology: observations --- dark ages, reionization, first stars}

%\section{Introduction}

%must use frequency structure to separate FGs from signal
%a certain amount of freq structure is imprinted onto smooth sources due to the frequency-dependent sampling function of an interferometer
%also by faraday rotation and the bandpass (citations)

%leakage is due to bandpass, frequency flagging, finite bandwidth. can be mitigated by subtraction in the delay spectrum (CLEAN), giving up on wedge modes, or subtraction in image space with foreground modeling, likely will have to give up on wedge modes too unless have incredible calibration and imaging fidelity, as LOFAR is attempting. Large risk of signal loss and calibration-induced transfer of spectral structure from long baselines to short ones

%hera is pursuing two relatively orthogonal power spectrum analyses (imaging and delay transform)

%the other papers in this series quantify the degree of spectral structure induced by the dish bandpass in measurement and modeling, we focus in this section on foreground leakage due to the finite bandwidth as a function of the beam response at different delays in the sky. Nithya discuss this is detail nithya15,nithya15b

%\citet{nithya15,nithya15b} 
%for a power spectrum analysis, note that these tests test how leakage varies as a function of the brightness of emission at different delays, not leakage due to beam frequency dependence (ie, either pattern or overall gain)

@@

We also plot (green dashed line) the delay spectrum after subtracting the visibilities computed with the $\theta\sim60^\circ$ cutoff measured beam from those using the full measured beam. This curve may be interpreted as the uncertainty in the ``pitchfork'' horizon brightening due to uncertainty in the beam horizon response, or equivalently as the delay spectrum residual foregrounds after subtracting foregrounds in the well modeled region of the sky. By construction, this subtraction leaves emission from the highest delay regions of the sky (near the horizon on opposite sides of the baseline), but also leaves some low delay emission on opposite sides of a line perpendicular to the baseline. However, this additional low delay emission near the horizon gets drowned out by that from near zenith where the beam is substantially stronger.

@@

\end{document}
-

>>>>

\documentclass{emulateapj}
%\documentclass[preprint]{aastex}

@@

\shorttitle{The HERA Dish: Beam Measurements and Science Implications}
\shortauthors{Neben et al.}

@@

\title{The Hydrogen Epoch of Reionization Array Dish: Beam Pattern Measurements and Science Implications}

@@

\author{Abraham R. Neben\altaffilmark{1},
Aaron Ewall-Wice\altaffilmark{1},
Nipanjana Patra\altaffilmark{2},
Nithyanandan Thyagarajan\altaffilmark{3},
James E. Aguirre\altaffilmark{4},
Zaki S. Ali\altaffilmark{2},
Judd Bowman\altaffilmark{3}
Carina Cheng\altaffilmark{2},
David R. DeBoer\altaffilmark{2}
Jacqueline N. Hewitt\altaffilmark{2},
Aaron Parsons\altaffilmark{2}}

\affil{\altaffilmark{1}MIT Kavli Institute, Massachusetts Institute of Technology, Cambridge, MA, 02139 USA}
\affil{\altaffilmark{2}Dept. of Astronomy, University of California, Berkeley, CA, USA}
\affil{\altaffilmark{3}Arizona State University, School of Earth and Space Exploration, Tempe, AZ 85287, USA}
\affil{\altaffilmark{4}Dept. of Physics and Astronomy, University of Pennsylvania, Philadelphia, PA}

@@

\keywords{instrumentation: interferometers --- techniques: interferometric --- cosmology: observations --- dark ages, reionization, first stars}

\section{Introduction}

basics of 21cm cosmology

must use frequency structure to separate FGs from signal
a certain amount of freq structure is imprinted onto smooth sources due to the frequency-dependent sampling function of an interferometer
also by faraday rotation and the bandpass (citations)

leakage is due to bandpass, frequency flagging, finite bandwidth. can be mitigated by subtraction in the delay spectrum (CLEAN), giving up on wedge modes, or subtraction in image space with foreground modeling, likely will have to give up on wedge modes too unless have incredible calibration and imaging fidelity, as LOFAR is attempting. Large risk of signal loss and calibration-induced transfer of spectral structure from long baselines to short ones

hera is pursuing two relatively orthogonal power spectrum analyses (imaging and delay transform)

the other papers in this series quantify the degree of spectral structure induced by the dish bandpass in measurement and modeling, we focus in this section on foreground leakage due to the finite bandwidth as a function of the beam response at different delays in the sky. Nithya discuss this is detail nithya15,nithya15b

\citet{nithya15,nithya15b} 
for a power spectrum analysis, note that these tests test how leakage varies as a function of the brightness of emission at different delays, not leakage due to beam frequency dependence (ie, either pattern or overall gain)

@@

We also plot (green dashed line) the delay spectrum after subtracting the visibilities computed with the $\theta\sim60^\circ$ cutoff measured beam from those using the full measured beam. This curve may be interpreted as the uncertainty in the ``pitchfork'' horizon brightening due to uncertainty in the beam horizon response, or equivalently as the delay spectrum residual foregrounds after subtracting foregrounds in the well modeled region of the sky (Neben et al. 2015b, submitted). By construction, this subtraction leaves emission from the highest delay regions of the sky (near the horizon on opposite sides of the baseline), but also leaves some low delay emission on opposite sides of a line perpendicular to the baseline. However, this additional low delay emission near the horizon gets drowned out by that from near zenith where the beam is substantially stronger.

@@

\end{document}
